Playing Games: A Case Study in Active Learning Applied to Game Theory

### 2015-06-28 paper/paper.tex
Adding rationalisation picture

\usepackage{fullpage} % Package to use full page
\usepackage{amsmath}
\usepackage{hyperref}

@@

A good description of the game and the human dynamics associated to the play is
given in \cite{Nagel1995}. The rules are as follows:

@@

The activity is similar to the activity described in
\cite{TheEconomicsNetwork2013}:

\begin{enumerate}
    \item Students are handed out copies of the form available at URL
    \item Students are explained the rules of the game and invited to play a
        first guess.
    \item After this the class is explained the rationalisation of the game
        (which uses best response dynamics to iteratively eliminate dominated
        strategies) as shown in Figure
        \ref{fig:rationalisation_of_two_thirds_game}.
    \item Students are invited to play one more time.
    \item Results are analysed and presented to the class for discussion.
\end{enumerate}

>>>>

\usepackage{fullpage} % Package to use full page
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}

@@

A good description of the game and the human dynamics associated to the play is
given in \cite{Nagel1995}.  The use of this game in teaching is not novel in
game theory \cite{TheEconomicsNetwork2013}
The rules are as follows:

@@

To make use of this game in class as an introduction to the concept of best
response dynamics students are handed a sheet of paper inviting them to write
down a first play. After this initial play, a discussion is had that
demonstrates that the equilibrium for this game is for all players to guess 0.
This is shown diagrammatically in Figure
\ref{fig:rationalisation_of_two_thirds_game}.
Following this discussion students are invited to play again and write down
their second guess.

\begin{figure}
    \begin{center}
        \begin{tikzpicture}
            % First level of play
            \node (0) at (0,0) {$0$};
            \node (100) at (10,0) {$100$};
            \draw [thick] (0) -- (100);
            \node [below] at (6.7,0) {$67$};

            % Getting rid of dominated strategies
            \foreach \x in {7, 7.3, 7.6, 7.9, 8.2, 8.5, 8.8, 9.1, 9.4}
            {
                \draw [blue!80, very thick] (\x,-.25) -- (\x + .2,.25);
            }
            \draw [very thick, blue!80] (9, -.5) edge[out=270,in=0,->] (7, -2);

                % Second level of play
                \node (0) at (0,-2) {$0$};
                \node (67) at (6.7,-2) {$67$};
                \draw [thick] (0) -- (67);
                \node [below] at (4.4,-2) {$44$};

                % Getting rid of dominated strategies
                \foreach \x in {4.7, 5, 5.3, 5.6, 5.9, 6.2}
                {
                    \draw [blue!60, very thick] (\x,-2.25) -- (\x + .2,-1.75);
                }
                \draw [very thick, blue!60] (6, -2.5) edge[out=270,in=0,->] (4.7, -4);

                    % Third level of play
                    \node (0) at (0,-4) {$0$};
                    \node (44) at (4.4,-4) {$44$};
                    \draw [thick] (0) -- (44);
                    \node [below] at (2.9,-4) {$29$};

                    % Getting rid of dominated strategies
                    \foreach \x in {3.2, 3.5, 3.8}
                    {
                        \draw [blue!40, very thick] (\x,-4.25) -- (\x + .2,-3.75);
                    }

                        % Final level of play
                        \node at (2, -5) {\dots};
                        \node (0) at (1,-6) [draw] {$0$};
                        \draw [very thick, blue!40] (3.4, -4.5) edge[out=270,in=0,->] (1.5, -6);

            \node at (8, -5) [draw] {Removing dominated strategies};
        \end{tikzpicture}
    \end{center}
    \caption{Equilibrium behaviour in the two thirds of the average
    game}\label{fig:rationalisation_of_two_thirds_game}
\end{figure}
